---
title: "CBI Regression tool"
date: "2023-03-17"
author: "Rich Schonenberg"
output:
  word_document: default
  pdf_document: default
subtitle: Utilizing publicly sourced Field Based Composite Burn Index (CBI) to Evaluate Accuracy of remotely sensed differenced Normalized Burn Ratio (dNBR) 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      include = TRUE,
                      eval= TRUE
                      )
```

Package Installs

```{r}
library(ggplot2)
library(mgcv)
library(readxl)
library(ggpubr)
library(ggpmisc)
```

#Aggregate and Clean CBI data

Navigate to USGS Science Base catalog and download Composite Burn Index (CBI) Data for the Conterminous US, Collected Between 1996 and 2018 (Fieldguide.mt.gov/displayES.aspx?id=2). Import Shape file into ArcPro to clip desired extent. load into R via clipboard or read Excel. Assess outliers or "Null" values, to have a clean Data frame


myCBI_data<-myCBI_data1[-111,]
myCBI_data <- read.table(file = "clipboard",   sep = "\t", header=TRUE)


```{r}
my_CBI_data <- read_excel(file.choose())
my_CBI_data$Cbi<-as.numeric(as.character(my_CBI_data$Cbi))
my_CBI_data$DNBR<-as.numeric(as.character(my_CBI_data$dNBR))
plot(my_CBI_data$Cbi, my_CBI_data$DNBR,xlab= "Composite Burn Index (CBI)", ylab = "Differenced Normalized Burn Ratio (dNBR)" )

```

Using GGplot and evaluating Models

```{r}
CBI_DBR_PLOT1<-ggplot(my_CBI_data)+aes(y=Cbi, x=dNBR)+geom_point()+
  labs(x="Composite Burn Index (CBI)", y="Differenced Normalized Burn Ratio (dNBR)")
plot(CBI_RDBR_PLOT1)
```


```{r}
ModelEval<-ggplot(my_CBI_data, aes(y = dNBR, x = Cbi)) + 
    geom_point() +
    geom_smooth(method = "gam", se = FALSE, aes(col = "GAM")) +
    geom_smooth(method = "loess", span = .2, se = FALSE, aes(col = "Loess")) +
    geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, aes(col = "Quadratic")) +
    geom_smooth(method = "lm", se = FALSE, alpha =.2, aes(col = "OLS")) +
    scale_color_viridis_d("Model", end = .75, option = "C") +
    labs(x="Composite Burn Index (CBI)", y="Differenced Normalized Burn Ratio (dNBR)")
ModelEval
```




looks like GAM is best fit
using linear model approach

```{r}
Quadraticmodel<-lm(Cbi ~ I(dNBR^2), data=my_CBI_data)
summary(Quadraticmodel)
```
```{r}
quadratic_model <- lm(dNBR ~ poly(Cbi, 2), data = my_CBI_data)

# Get coefficients of the quadratic model
coefficients <- coef(quadratic_model)

# Extract coefficients
intercept <- coefficients[1]
coeff_cbi <- coefficients[2]
coeff_cbi2 <- coefficients[3]

# Print the equation of the quadratic model
cat("Equation of the quadratic model: ")
cat("y =", round(intercept, 3), "+", round(coeff_cbi, 3), "* Cbi +", round(coeff_cbi2, 3), "* Cbi^2")
```

r-squared is only .60, lets try other GAM models

```{r}
gam_mod<-gam(Cbi~s(DNBR),data=my_CBI_data)
summary(gam_mod)
```

Slightly better,.61
GAM approach, Add to graph

```{r}
CBI_RDBR_PLOT2 <-ggplot(my_CBI_data, aes(x = Cbi, y = dNBR)) + 
    geom_point() +
    geom_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1,)+
    scale_color_viridis_d("Model", end = .75, option = "C")+
    labs(x="Composite Burn Index (CBI)", y="Differenced Normalized Burn Ratio (dNBR)")+
    ggtitle("CBI Values by Remotely Sensed dNBR Values for CONUS Dry Western Forest")+
    stat_poly_eq()+ 
    theme(plot.title = element_text(hjust = .5))+
    theme(text = element_text(size = 20))
plot(CBI_RDBR_PLOT2)
```

```{r}
rsquared_unadjusted <- summary(gam_mod)$r.sq[1]
CBI_RDBR_PLOT3 <- ggplot(my_CBI_data, aes(x = Cbi, y = DNBR)) + 
     geom_point() +
    geom_smooth(method = "gam", formula = y ~ x + s(x), size = 1, se = FALSE) +
     scale_color_viridis_d("Model", end = .75, option = "C") +
     labs(x = "Composite Burn Index (CBI)", y = "Differenced Normalized Burn Ratio (dNBR)") +
     ggtitle("CBI Values by Remotely Sensed dNBR Values for CONUS Dry Western Forest") +
     annotate("text", x = max(my_CBI_data$Cbi), y = min(my_CBI_data$DNBR), 
              label = paste("Unadjusted R-squared =", round(rsquared_unadjusted, 3)), 
              hjust = 1, vjust = 0) +
     theme(plot.title = element_text(hjust = .5)) +
     theme(text = element_text(size = 20))
CBI_RDBR_PLOT3
```

same thing

```{r}
gam_mod <- gam(DNBR ~ s(Cbi), data = my_CBI_data)

# Calculate unadjusted R-squared
rsquared_unadjusted <- round(summary(gam_mod)$r.sq[1], 3)

# Extract GAM formula
gam_formula <- as.character(gam_mod$formula)

# Create the scatter plot with GAM model overlay
CBI_RDBR_PLOT3 <- ggplot(my_CBI_data, aes(x = Cbi, y = DNBR)) + 
     geom_point() +
     geom_smooth(method = "gam", formula = y ~ s(x), size = 1, se = FALSE, color = "blue") +
     scale_color_viridis_d("Model", end = .75, option = "C") +
     labs(x = "Composite Burn Index (CBI)", y = "Differenced Normalized Burn Ratio (dNBR)") +
     ggtitle("CBI Values by Remotely Sensed dNBR Values for CONUS Dry Western Forest") +
     annotate("text", x = max(my_CBI_data$Cbi), y = min(my_CBI_data$DNBR), 
              label = paste("Unadjusted R-squared =", rsquared_unadjusted), 
              hjust = 1, vjust = 0) +
     annotate("text", x = max(my_CBI_data$Cbi), y = min(my_CBI_data$DNBR) + 10, 
              label = paste("GAM Formula:", gam_formula), 
              hjust = 1, vjust = 0) +
     theme(plot.title = element_text(hjust = .5),
           text = element_text(size = 20))

CBI_RDBR_PLOT3 # Display the plot
```




Extra code
 
```{r}
CBI_RDBR_PLOT4 <- ggplot(my_CBI_data, aes(x = Cbi, y = DNBR)) + 
     geom_point() +
     geom_smooth(method = "gam", formula = y ~ x + s(x), size = 1, se = FALSE) +
     scale_color_viridis_d("Model", end = .75, option = "C") +
     labs(x = "Composite Burn Index (CBI)", y = "Differenced Normalized Burn Ratio (dNBR)") +
    ggtitle("CBI Values by Remotely Sensed dNBR Values for CONUS Dry Western Forest") +
     theme(plot.title = element_text(hjust = .5)) +
     theme(text = element_text(size = 20))
 CBI_RDBR_PLOT4 
```

making a threshold table..

```{r}
model <- gam(Cbi ~ s(DNBR), data = my_CBI_data)
cbi_values <- seq(min(my_CBI_data$Cbi), max(my_CBI_data$Cbi), length.out = 100)
predicted_dnbr <- predict(model, newdata = data.frame(Cbi = cbi_values), type = "response")
threshold_table <- data.frame(Cbi = cbi_values, Predicted_DNBR = predicted_dnbr)
hreshold_table$Severity <- cut(threshold_table$Predicted_DNBR,
                                breaks = c(min(my_CBI_data$DNBR), 1.24, 2.24, max(my_CBI_data$DNBR)),
                                labels = c("Low", "Moderate", "High"))
print(threshold_table)



```



##just using AI instead of old stuff quadratic eq

```{r}
model_quad <- lm(DNBR ~ Cbi + I(Cbi^2), data = my_CBI_data)

# Summary of the quadratic regression model
summary(model_quad)

# Plot the quadratic regression line
plot(my_CBI_data$Cbi, my_CBI_data$DNBR, main = "Scatterplot of Cbi vs DNBR with Quadratic Regression Line")
curve(predict(model_quad, newdata = data.frame(Cbi = x)), add = TRUE, col = "red")

# Residuals vs Fitted plot
plot(model_quad, which = 1)

# Normal Q-Q plot
plot(model_quad, which = 2)

# Scale-Location plot (Square root of standardized residuals vs fitted values)
plot(model_quad, which = 3)

# Residuals vs Leverage plot
plot(model_quad, which = 5)
```



```{r}
intercept <- 33.924
coef_Cbi <- 23.867
coef_Cbi_squared <- 54.171

# Values of CBI for estimation
Cbi_values <- c(1.25, 2.25)

# Calculate estimated DNBR values
DNBR_est <- intercept + coef_Cbi * Cbi_values + coef_Cbi_squared * Cbi_values^2

# Display the estimated DNBR values
data.frame(Cbi = Cbi_values, DNBR_est = DNBR_est)
```








#good scatterplot...

```{r}
scatterplot <- ggplot(my_CBI_data, aes(x = Cbi, y = DNBR)) +
  geom_point(color = "black", size = 1) +  # Smaller black scatterplot points
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "#E74C3C") +  # Red quadratic regression line
  labs(x = "Composite Burn Index (CBI)", y = "Differenced Normalized Burn Ratio (dNBR)") +  # Axis labels
  ggtitle("Relationship Between Composite Burn Index (CBI) and \n Remotely Sensed dNBR for Dry Western Coniferous Forests") +  # Plot title (wrapped)
  theme_minimal() +  # Minimal theme for cleaner appearance
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),  # Bold and centered main title, adjusted font size
        axis.title = element_text(face = "bold", size = 14),  # Bold axis labels, adjusted font size
        axis.text = element_text(size = 12),  # Adjusted font size for axis numbers/ticks
        panel.background = element_rect(fill = "grey90"),  # Shaded grey background grid
        panel.grid.major = element_line(color = "grey70", size = 0.5),  # Grey grid lines
        panel.grid.minor = element_blank()) +  # Remove minor grid lines
  annotate("text", x = min(my_CBI_data$Cbi), y = max(my_CBI_data$DNBR), hjust = 0, vjust = 1,
           label = bquote("dNBR = 34 + 24 * Cbi + 54 * Cbi²"), size = 4) +  # Annotation for model equation
  annotate("text", x = min(my_CBI_data$Cbi), y = max(my_CBI_data$DNBR) - 80, hjust = 0, vjust = 1,
           label = "R² = 0.62", size = 4)  # Annotation for R-squared value

# Save the plot to the specified directory
ggsave(filename = "C:\\Users\\z44h489\\OneDrive - Montana State University\\Rich's Thesis folder\\CONUSRXSTUDY\\scatterplot.png", 
       plot = scatterplot, 
       width = 8, 
       height = 6, 
       units = "in", 
       dpi = 300)

# Print the plot
print(scatterplot)
```

