---
title: "Specific_RASter_clips"
author: "Rich"
date: "2024-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("raster")
library(raster)
library(sf)
library(dplyr)
```


## Making RX polygon mosiacs while preserving overlaps

```{r}
# Set the directory path
polygon_dir <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSRX/BURNDBY"
# List all shapefiles in the directory
polygon_files <- list.files(polygon_dir, pattern = "\\.shp$", full.names = TRUE)
# Read each shapefile into an sf object and store them in a list
polygon_list <- lapply(polygon_files, st_read)
```


```{r}
# Combine all polygons into one
combined_polygon <- do.call(rbind, polygon_list)
# preserve attribute information, you can create a new attribute to differentiate between the original polygons
combined_polygon$source <- factor(rep(polygon_files, sapply(polygon_list, nrow)))
```


```{r}
# Specify the output shapefile path
output_shapefile <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSRX"

# Write the combined polygon layer to a shapefile
st_write(combined_polygon, output_shapefile, driver = "ESRI Shapefile")

```

## Making WF polygon mosiacs while preserving overlaps

```{r}
polygon_dir <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/CONDENSED/BURN BODY"

# List all shapefiles in the directory
polygon_files <- list.files(polygon_dir, pattern = "\\.shp$", full.names = TRUE)

# Read each shapefile into an sf object and store them in a list
polygon_list <- lapply(polygon_files, st_read)

# Combine all polygons into one
combined_polygon <- do.call(rbind, polygon_list)

# Optionally, if you want to preserve attribute information, you can create a new attribute to differentiate between the original polygons
combined_polygon$source <- factor(rep(polygon_files, sapply(polygon_list, nrow)))

# Specify the output shapefile path
output_shapefile <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/CONDENSED/combined_polygons.shp"

# Write the combined polygon layer to a shapefile
st_write(combined_polygon, output_shapefile, driver = "ESRI Shapefile")
```


#OVerlapp instersectoion 

```{r}
combined_polygons <- st_read("C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/CONDENSED/combined_polygons.shp")
CONUSRX <- st_read("C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSRX/CONUSRX.shp")

# Perform intersection to find overlapping polygons
overlap <- st_intersection(combined_polygons, CONUSRX)

# Check if there are any overlapping polygons
if (nrow(overlap) == 0) {
  stop("No overlapping polygons found.")
} else {
  # Create a new attribute indicating overlap
  overlap$overlap <- "yes"
  
  # Write the overlapping polygons to a new shapefile
  output_shapefile <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/overlap_polygons.shp"
  st_write(overlap, output_shapefile, driver = "ESRI Shapefile")
}
```


##result will contain the polygons from combined_polygons with the overlapping areas replaced by overlap_polygons.


```{r}
overlap <- st_intersection(combined_polygons, overlap)
non_overlap <- st_difference(combined_polygons, overlap)
result <- st_union(non_overlap, overlap)

```


##Wildfire DNBR data


```{r}
polygon_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/CONDENSED/BURN BODY"
raster_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/CONDENSED/DNBR"
output_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/Clipped_Rasters"
```



```{r}
output_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/Clipped_Rasters"
if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
}
```

# List files in the directory

```{r}
polygon_files <- list.files(polygon_path, full.names = TRUE, pattern = "\\.shp$", recursive = TRUE)
raster_files <- list.files(raster_path, full.names = TRUE, pattern = "\\.tif$", recursive = TRUE)
```

# Iterate through each pair of raster and polygon files

```{r}
for (i in 1:length(raster_files)) {
  # Load raster and polygon data
  raster_data <- raster(raster_files[i])
  polygon_data <- shapefile(polygon_files[i])
  
  # Clip raster using polygon
  clipped_raster <- mask(raster_data, polygon_data)
  
  # Define output filename
  output_filename <- file.path(output_path, paste0("clipped_", basename(raster_files[i])))
  
  # Save clipped raster to output directory
  writeRaster(clipped_raster, filename = output_filename, format = "GTiff", overwrite = TRUE)
  
  # Print progress
  print(paste("Clipping complete for:", basename(raster_files[i])))
}
```


#clipall rasters by bimodal tree cover from raster 

```{r}
raster_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/Clipped_Rasters"
forest_cover_path <- "C:/Users/z44h489/OneDrive - Montana State University/Documents/Desktop/Biophysical Model Data/CONUSWF/Dry_Western_Con_BiModal.tif"

# List DNBR raster files
raster_files <- list.files(raster_path, full.names = TRUE, pattern = "\\.tif$", recursive = TRUE)

# Read forest cover raster
forest_cover <- raster(forest_cover_path)

# Iterate through each DNBR raster file
for (raster_file in raster_files) {
  # Read DNBR raster
  dnbr_raster <- raster(raster_file)
  
  # Clip DNBR raster to forest cover extent
  clipped_raster <- crop(dnbr_raster, extent(forest_cover))
  
  # Write clipped raster to output directory
  writeRaster(clipped_raster, filename = raster_file, format = "GTiff", overwrite = TRUE)
  
  # Print progress
  print(paste("Clipping complete for:", basename(raster_file)))
}
```


